sentiment-analysis

### 2016-08-06 eda/sentiment-analysis.Rmd
plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(jsonlite)
library(stringr)
library(ggplot2)
library(dplyr)
library(tidytext)
library(tm)
```

@@

```{r fig.height = 7, fig.width = 7}
summaries %>% 
  ggplot(aes(reviews, average_star, color = score)) +
  geom_point() +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
  scale_x_log10(limits = c(200, 100000), 
                breaks = c(1000, 10000), labels = c(1000, 10000)) +
  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
  scale_color_gradient2(low = "red", high = "blue", midpoint = 0, mid = "gray") +
  labs(x = "# of reviews",
       y = "Average Stars",
       color = "AFINN") +
  theme_bw()
```
Blue words mostly lie above the line and red words lie below so reveiw text is a pretty good predictor of business rating. Let's see how accurate it was.

```{r}
positive <- summaries %>% 
  filter(score > 0)
negative <- summaries %>% 
  filter(score < 0)
above <- positive %>% 
  filter(average_star >= mean(reviews$stars))
below <- negative %>% 
  filter(average_star <= mean(reviews$stars))
percent_pos <- nrow(above) / nrow(positive)
percent_neg <- nrow(below) / nrow(negative)
print(str_c("Positivity Accuracy: ", percent_pos))
print(str_c("Negativity Accuracy: ", percent_neg))
```
64.23% of positive words lie above the mean average rating! There's definitely a positive correlation between word positivity in text reviews and Yelp business star ratings. Word negativity is even better at 87.24% accuracy of negative words lying below the mean average rating.

What's the accuracy for words that are +5 or -5? Do they lead to 5-star ratings?
```{r}
pos_five <- summaries %>% filter(score == 5)
neg_five <- summaries %>% filter(score == -5)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(jsonlite)
library(stringr)
library(ggplot2)
library(dplyr)
library(tidytext)
library(tm)
library(ggrepel)
source("../functions/PercentAccuracy.R")
```

@@

```{r fig.height = 7, fig.width = 7}
summaries %>% 
  ggplot(aes(reviews, average_star, color = score)) +
  geom_point() +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
  scale_x_log10(limits = c(200, 100000), 
                breaks = c(1000, 10000), labels = c(1000, 10000)) +
  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
  scale_color_gradient2(low = "red", high = "blue", 
                        midpoint = 0, mid = "grey") +
  labs(x = "# of reviews",
       y = "Average Yelp Stars",
       color = "Valence Score") +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
  theme_bw()
```

Blue words mostly lie above the line and red words lie below so reveiw text is a pretty good predictor of business rating. Let's see how accurate it was.

```{r}
positive <- summaries %>% 
  filter(score > 0)
negative <- summaries %>% 
  filter(score < 0)
percent_pos <- PercentAccuracy(positive)
percent_neg <- 1 - PercentAccuracy(negative)
print(str_c("Positivity Accuracy: ", percent_pos))
print(str_c("Negativity Accuracy: ", percent_neg))
```
64.23% of positive words lie above the mean average rating! There's definitely a positive correlation between word positivity in text reviews and Yelp business star ratings. Word negativity is even better at 87.24% accuracy of negative words lying below the mean average rating.

```{r fig.height = 7}
summaries %>% 
  arrange(desc(reviews)) %>% 
  ggplot(aes(score, average_star)) +
  geom_point(aes(size = reviews)) +
  geom_text(aes(label = word), vjust = 1, hjust = 1, check_overlap = TRUE) +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Valence Score") +
  ylab("Average Yelp Stars") +
  labs(title = "Average Yelp Star Rating vs. Valence Score") +
  scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
  expand_limits(x = -6)
```
